---
title: "Lab 1"
author: "Alejandra Garcia Isaza"
date: "4/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Run the above code

```{r}
set.seed(123) # Set random number generation

m <- lm(mpg ~ hp + cyl + drat, mtcars)

l <- list(a = list(m = matrix(1:12, ncol = 3),
                   v = 1:7),
          b = data.frame(student = 1:15,
                         score = rnorm(15, 100, 10)))
```


From the model results:
Extract the qr tolerance (tol).
Extract the term labels from the model.
hint: Use str to inspect the list. This one is tricky and involves pulling an attribute from an attribute.
From the list
Use at least two different methods to extract m.
Extract the third column of m. Maintain the dimensions (matrix structure).
Extract the score for student 7.
Loops
Use the “airquality” dataset, which is part of base R. Split it by Month

Use a for loop to calculate the mean Ozone by month (remember to remove missing data from the calculation)

Replicate this calculation with lapply, sapply, and vapply

Produce separate plots showing the relation between Ozone and Solar.R for each month (with a single loop).

Use a for loop to save the plots to a folder on your computer